Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-11-24 Journal1/paper1TNSM/pr.tex
change paper 1 after reviewing tnsm template 13 page

 %\pdfoutput=1
%\documentclass[conference]{IEEEtran}
\documentclass[journal,draftcls,onecolumn,12pt,twoside]{IEEEtranTCOM}
\normalsize
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\usepackage{algcompatible}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength{\columnsep}{11mm}
\captionsetup{font=footnotesize}
\captionsetup[figure]{font=small}
\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
\newcommand{\abstracttextfont}{\normalfont\small}
\setlength{\belowcaptionskip}{-25pt}
\setlength{\dbltextfloatsep}{-20pt}
\begin{document}

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
 }

\maketitle
\pagenumbering{gobble}
\vspace*{-6em}
\begin{abstract}
\vspace*{-1.5em}
Taking advantage of virtual radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility, openness, reduces operational costs, and agile deployment. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of service aware baseband resource allocation and virtual network function (VNF) activation in O-RAN system using network slicing to isolate different types of services.
The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
The proposed method is validated via simulations which illustrate a higher data rate and lower end-to-end delay compared to existing methods. 
\end{abstract}
\begin{IEEEkeywords}
Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing.
\end{IEEEkeywords}
\section{Introduction} 
One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. 
Network slicing can support the heterogeneity of services by allocating different resources to each slice serving specific services to guarantee QoS, and isolating each service from the other services.
A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
5G wireless systems have talked about supporting three generic services in recent years, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughput coverage.
URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

@@

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
The purpose of this study is to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presents of the three generic service types introduced in 5G using RAN slicing.
In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}

\begin{figure*}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.6]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

@@

In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and URLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}

 There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.
Assume we have $K$ physical resource blocks (PRBs) in this system.
All $K$ PRBs can be assigned to all UEs in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

%Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq1}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to the $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)

@@

T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\

@@

T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},\\

@@

Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.

@@

 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\

@@

&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\

@@

Another solution is to remove the simulations in the mont-Carlo that do not converge.

@@

@@

>>>>

 %\pdfoutput=1
%\documentclass[conference]{IEEEtran}
\documentclass[lettersize,journal]{IEEEtran}
\normalsize
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\captionsetup{font=footnotesize}
\usepackage{algcompatible}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
%\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmicx}
%\usepackage{algorithmic,algorithm2e,float}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength{\columnsep}{11mm}
\captionsetup{font=footnotesize}
\captionsetup[figure]{font=small}
\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
\newcommand{\abstracttextfont}{\normalfont\small}
\setlength{\belowcaptionskip}{-10pt}
%\setlength{\dbltextfloatsep}{-20pt}
\begin{document}

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
Taking advantage of virtual radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility, openness, reduces operational costs, and agile deployment. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of service aware baseband resource allocation and virtual network function (VNF) activation in O-RAN system using network slicing to isolate different types of services.
The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
The proposed method is validated via simulations which illustrate a higher data rate and lower end-to-end delay compared to existing methods. 
\end{abstract}
\begin{IEEEkeywords}
Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing.
\end{IEEEkeywords}
\section{Introduction} 
One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. 
Network slicing can support the heterogeneity of services by allocating different resources to each slice serving specific services to guarantee QoS, and isolating each service from the other services.
A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
5G wireless systems have talked about supporting three generic services in recent years, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughput coverage.
URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

@@

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
The purpose of this study is to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presents of the three generic service types introduced in 5G using RAN slicing.
In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}  
\begin{figure*}
    \includegraphics[scale = 0.45]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

@@

In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and URLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}

There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have 
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system.

Assume we have $K$ physical resource blocks (PRBs) in this system.
All $K$ PRBs can be assigned to all UEs in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

%Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq1}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to the $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{H \: k} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}
\end{equation}

The channel state information is imperfect. So, the channel gain is known with errors; the imperfection of channel estimation is shown as
$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$.
$\Delta \boldsymbol{h}_{r,u(s,i)}$ indicates the estimating error vector with a Gaussian distribution of
$\Delta \boldsymbol{h}_{r,u(s,i)}\backsim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$.
where $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$

Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)

@@

T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}. 

@@

T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},

@@

Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ (based on the priority of its hosting service) where $\sum_{s=1}^S \delta_s =1$.

@@

 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.

@@

&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.

@@

Another solution is to remove the simulations in the Monte-Carlo that do not converge.

@@

\begin{figure*}%[!tbp]

@@

\end{figure*}
